# CV
A PDF version can be downloaded [here](https://github.com/reitancorp/cv/raw/master/cv/cv.pdf).

## Experience

Resident physician, Cardiology \| 2020 - Current\
Danderyd Hospital, Dept. of Cardiology \| Stockholm, Sweden

Researcher \| 2020 - Current\
Karolinska institutet, Institution for Clinical Sciences Danderyd Hospital \| Stockholm, Sweden

Surgeon, licensed physician \| 2018 - 2020\
Karolinska University Hospital, Dept. of Cardiothoracic surgery \| Stockholm, Sweden

Surgeon, licensed physician \| 2017 - 2018\
Scania University Hospital, Dept. of Cardiothoracic surgery \| Lund, Sweden

Medical internship, reseach profile (AT) \| 2015-2017\
Scania University Hospital \| Malmö, Sweden

Junior surgeon \| 2014 - 2015\
Karolinska University Hospital, Dept. of Cardiothoracic surgery \| Stockholm, Sweden

Junior Doctor \| 2014-2014\
Scania University Hospital, Emergency department \| Lund, Sweden

## Education

PhD, Cardiology \| 2014-2018\
Lund University \| Stockholm, Sweden

Medical School, MD \| 2008-2014\
Lund University \| Lund, Sweden

## Publications
```{r}
#| include: false
library(tidyverse)
library(scholar)
```


```{r}
#| echo: false
#| warning: false
#| message: false
#| output: asis
## Publications - change google id here
pubs <- scholar::get_publications("S3TOd7gAAAAJ") %>% tibble() %>%
  mutate(url = scholar::get_article_scholar_url("S3TOd7gAAAAJ", pubid = pubid)) %>%
  arrange(desc(year))

# manual removal of some entries
remove_ <- c("Early Subjective Improvement of Exercise Capacity is an Indpendent Predictor of Long Term Survival in Cardiac Resynchronization Therapy Patients",
             "Long-term results of cardiac resynchronization therapy: A comparison between CRT-pacemakers versus primary prophylactic CRT-defibrillators (vol 38, pg 758, 2015)",
             "3291 Achieved biventricular pacing during the first year of follow-up predicts long-term outcome in patients with heart failure treated with cardiac resynchronization therapy",
             "P1950 CHA2DS2-VASC score in a cohort of CRT patients",
             "CHA2DS2-VASC score in a cohort of CRT patients",
             "Ventricular high rate episodes predict increased mortality in heart failure patients treated with CRT (vol 49, pg 20, 2015)",
             "P5683 Incremental hazard associated with the degree of advanced intaratrial block in cardiac resynchronization therapy treated heart failure patients",
             "Reclassification of Treatment Strategy With Instantaneous Wave-Free Ratio and Fractional Flow Reserve",
             "Positive Response to Cardiac Resynchronization Therapy-The Role of NTproBNP",
             "Incremental hazard associated with the degree of advanced intaratrial block in cardiac resynchronization therapy treated heart failure patients",
             "Left ventricular systolic dysfunction after acute myocardial infarction is associated with a high symptom burden and worse secondary prevention",
             "Comparison of sodium-glucose co-transporter-2 inhibitors and glucagon-like peptide-1 receptor agonists in myocardial infarction patients with type 2 diabetes"
)
pubs <- pubs %>% filter(!title %in% remove_) %>%
  # remove on pubid
  filter(!pubid == "QIV2ME_5wuYC")

# add information to thesis
pubs <- pubs %>%
  mutate(journal = ifelse(pubid == "WF5omc3nYNoC", 'Lund University, Thesis', journal))


# format for markdown
pubs <- pubs %>% 
  mutate(out = paste0("[", author, "(", year, "). ", title, ". *", journal, "*. ", number,"](", url, ")\n\n")) %>%
  select(title, out)

cat(pubs$out)
```
